\speculake: Hiding Malware in Speculative Execution

### 2018-05-06 paper/figures.tex

>>>>

\newcommand{\FigSpasmModel}{
\begin{figure}[b]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/spasm_model}
    \caption{This model describes the VM control flow. An encrypted SPASM binary 
        stored in dead code or data accessible to \textit{Speculative Computation} 
        is decrypted  and then returned through the primitive. The SPASM 
        \textit{Resultant Computation} performs the SPASM emulation to update the 
        process state before the next instruction is decrypted.}
    \label{fig:spasm_model}
\end{figure}
}

### 2018-05-06 paper/implementation.tex
Figure updates for speculative measurements

\begin{figure}[t]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/spec_bandwidth}
    \caption{Using the speculative primitive to decrypt 1KB of data
        we have classified the speed at which data can be exfiltrated
        from the speculative world. Varying the width of the channel 
        results in competing performance factors -- decreasing the 
        number of loops vs decreased size of the probe space.}
    \label{fig:spec_bandwidth}
\end{figure}

% implementation 
%   Key Schedule expansion / obfuscation
%
% you can speculatively execute AES instructions

@@

\begin{figure}[b]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/spasm_model}
    \caption{This model describes the VM control flow. An encrypted SPASM binary 
        stored in dead code or data accessible to \textit{Speculative Computation} 
        is decrypted  and then returned through the primitive. The SPASM 
        \textit{Resultant Computation} performs the SPASM emulation to update the 
        process state before the next instruction is decrypted.}
    \label{fig:spasm_model}
\end{figure}

>>>>

\FigSpecBandwidth
% implementation 
%   Key Schedule expansion / obfuscation
%
% you can speculatively execute AES instructions

@@

\FigSpasmModel
